### 2021-03-15 sections/experience.tex
Update experience.tex

\begin{cventries}
\cventry
{Instructor} 
{Universidad de Santiago} 
{Santiago, Chile} 
{2019 - on leave}
{Department of Public Administration and Policy, Faculty of Economics and Management}\vspace{1.5mm}

\cventry
{Adjunct Professor} 
{Universidad de Santiago} 
{Santiago, Chile} 
{2014 - 2018}
{Department of Public Administration and Policy, Faculty of Economics and Management} \vspace{1.5mm}

\cventry
{Consultant} 
{United Nations Development Programme} 
{Santiago, Chile} 
{2016 - 2017}
{Democratic Governance Programme} \vspace{1.5mm}

>>>>

\begin{cventries}
\cventry
{Instructor Professor} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2019 - on leave}
{Management and Public Policies Department, Faculty of Administration and Economics}\vspace{1.5mm}

\cventry
{Adjunct Professor} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2014 - 2018}
{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}

\cventry
{Consultant} 
{United Nations Development Programme (UNDP)} 
{Santiago, Chile} 
{2016 - 2017}
{Democratic Governance Programme} \vspace{1.5mm}
